Fig2

### 2020-02-26 analysis/figure-2.Rmd
now with table 1 in readme

table1 <- allDEG %>%
  filter(gene %in% candidategenes,
         comparison != "control_bldg") %>%
    arrange(gene) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, bldg_lay, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17,inc.d17_hatch, hatch_n5, n5_n9)  %>%
  arrange( tissue, sex)
table1

table2 <- allDEG2 %>%
  filter(gene %in% candidategenes) %>%
  arrange(gene) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  arrange( tissue, sex)
table2

>>>>

table1 <- allDEG %>%
  filter(gene %in% candidategenes,
         comparison != "control_bldg") %>%
    arrange(gene) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  select(sex, tissue, bldg_lay, lay_inc.d3, inc.d3_inc.d9,
        inc.d9_inc.d17,inc.d17_hatch, hatch_n5, n5_n9)  %>%
  arrange( tissue, sex)
kable(table1)

table2 <- allDEG2 %>%
  filter(gene %in% candidategenes) %>%
  arrange(gene) %>%
  group_by(sex, tissue, comparison) %>%
  summarize(genes = str_c(gene, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = genes ) %>%
  arrange( tissue, sex)
table(table2)
